---
title: "Final"
author: 'Tyler Scott, Daniel Gordon'
output: html_document
date: "2022-10-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(tidyverse, dplyr)
complaint_data <- read.csv('allegations.csv')
```

# Introduction

For years there has been tension between the police force in the United States and its citizens. 
Factors of this tension has been highly debated, but through data analysis we can more accurately pinpoint specific elements
that can lead to this tension. Notably physical difference between the people and the police in an authoritative position. 
We will be looking at the external factors that can lead to these tensions and how they correlate to the severity of allegations
against the police. 

# Data Description

The data set we will be using has 33,368 complaints against against police in the United States between 1985 and 2020.
It also keeps track of multiple aspects of the officer and the citizen complaining. This includes their race, gender,  

```{r cars}

```

